Sorting by Reversals

### 2020-07-08 slides.tex
add citation
update slides

\begin{definition}
Let $i \sim j$ if $|i - j| = 1$. \par\pause
A pair of consecutive elements $\pi_i$ and $\pi_j$ is
\begin{itemize}
    \item an \b{adjacency} if $\pi_i \sim \pi_j$; and
    \item a \b{breakpoint} if $\pi_i \not\sim \pi_j$.
\end{itemize} \par\pause\spadding
$b(\pi)$ denotes the number of breakpoints in $\pi \in S_n$.
\end{definition}\pause\padding

@@

Observations:
\begin{itemize}
    \item Every connected component $A$ arising from k different alternating cycles of $G(\pi)$, eventually reduces to a two cycle.\pause
    \item There exists an elimination sequence of $A$ with $k$ $2$-reversals and remaining $1$-reversals.\pause
    \item An unoriented connected component requires one initial $0$-reversal.
\end{itemize}\spadding\pause

@@

\begin{proof}[Proof (cont.)]
Left to show: $k+l+m-v \geq \frac{c_2(\pi)}{2}$. \pause We know that
\begin{enumerate}
    \item $k+l+m \geq \left\lceil \frac{y}{2} \right\rceil + z$ as $\left\lceil \frac{y}{2} \right\rceil + z$ is the number of selected $2$-cycles by $M$\pause;
    \item $v \leq \left\lfloor \frac{z}{2} \right\rfloor$ as every unoriented component representing a $2$-cycle represents at least one more alternating cycle (lemma \ref{lem:7})\pause; and
    \item $|M| = y+z \geq c_2(\pi)$.
\end{enumerate}\pause
\begin{align*}
    k+l+m-v &\geq \left\lceil \frac{y}{2} \right\rceil + z - v                                          & (1) \\ \pause
            &\geq \left\lceil \frac{y}{2} \right\rceil + z - \left\lfloor \frac{z}{2} \right\rfloor     & (2) \\ \pause
            &= \left\lceil \frac{y}{2} \right\rceil + \left\lceil \frac{z}{2} \right\rceil \\ \pause
            &\geq \frac{c_2(\pi)}{2}                                                                    & (3)
\end{align*}
\end{proof}

@@

Run time: $O(n^4)$, can be improved to $O(n^2)$.\spadding

>>>>

\begin{definition}
Let $i \sim j$ if $|i - j| = 1$. \par
A pair of consecutive elements $\pi_i$ and $\pi_j$ is
\begin{itemize}
    \item an \b{adjacency} if $\pi_i \sim \pi_j$; and
    \item a \b{breakpoint} if $\pi_i \not\sim \pi_j$.
\end{itemize} \par\pause\spadding
$b(\pi)$ denotes the number of breakpoints in $\pi \in S_n$.
\end{definition}\pause\padding

@@

Observations:
\begin{itemize}
    \item Every connected component $A$ arising from $k$ different alternating cycles of $G(\pi)$, eventually reduces to $k$ $2$-cycles.\pause
    \item There exists an elimination sequence of $A$ with $k$ $2$-reversals and remaining $1$-reversals.\pause
    \item An unoriented connected component requires one initial $0$-reversal.
\end{itemize}\spadding\pause

@@

\begin{proof}[Proof (cont.)]
Left to show: $k+l+m-v \geq \frac{c_2(\pi)}{2}$. \pause We know that
\begin{enumerate}
    \item $k+l+m \geq \left\lceil \frac{y}{2} \right\rceil + z$ as $\left\lceil \frac{y}{2} \right\rceil + z$ is the number of selected $2$-cycles in $C$\pause;
    \item $v \leq \left\lfloor \frac{z}{2} \right\rfloor$ as every unoriented component representing a $2$-cycle represents at least one more alternating cycle (lemma \ref{lem:7})\pause; and
    \item $|M| = y+z \geq c_2(\pi)$.
\end{enumerate}\pause
\begin{align*}
    k+l+m-v &\geq \left\lceil \frac{y}{2} \right\rceil + z - v                                          & (1) \\ \pause
            &\geq \left\lceil \frac{y}{2} \right\rceil + z - \left\lfloor \frac{z}{2} \right\rfloor     & (2) \\ \pause
            &= \left\lceil \frac{y}{2} \right\rceil + \left\lceil \frac{z}{2} \right\rceil \\ \pause
            &\geq \frac{c_2(\pi)}{2}                                                                    & (3)
\end{align*}
\end{proof}

@@

Run time: $O(n^4)$, can be improved to $O(n^2)$ (\citeauthor*{Kaplan1997}).\spadding
